Complex Analysis of Askaryan Radiation: Towards UHE-$\nu$ energy Reconstruction via the Hilbert Envelope of Observed Signals

### 2025-07-03 template.tex
made updates to manuscript reflecting changes in s * r

The imaginary part of $I$ is proportional to \textit{Dawson's integral, $D(x)$:}

@@

Let $b = jq$, and $w(q)$ be the \textit{Faddeeva function}.  The integral becomes

@@

\mathcal{E}_{r * s}(t) = \frac{1}{2} | r_a(t) * s_a(t) |

@@

\item Two examples of comparisons of Eq. \ref{eq:final} to the convolution of $s(t)$ and $r(t)$ are given in Fig. \ref{fig:fig1} below.
\begin{figure}[hb]
\clearpage

@@

Let $b=x+\frac{1}{2}z$, and $a = -jb$.  Completing the square in the exponent of $I(x,z)$ gives

@@

I(x,z) = \frac{\sqrt{\pi}}{2} w(a)

@@

where $w(a)$ is the Faddeeva function.  Note that the Faddeeva function is \textit{entire}, meaning the $\Re\lbrace \rbrace$ operator and differentiation commute.  Inserting this result into Eq. \ref{eq:conv_sr}, and distributing the $\Re\lbrace \rbrace$ operator to the instances of $I(x,z)$, gives

@@

s * r = \\ -\sqrt{\pi}R_0 E_0 \sigma_t^2 \left(xe^{-x^2} \Re\left\lbrace w(a)\right\rbrace - \frac{1}{2}e^{-x^2} \frac{d\Re\lbrace w(a)\rbrace}{dx} \right)

@@

The Faddeeva function may be split into real and imaginary parts via the \textit{Voigt functions}:
w(a) &= U(p,q) + jV(p,q) \\
p &= 

>>>>

The imaginary part of $I$ is proportional to \textit{Dawson's integral, $D(x)$} \cite{NIST:DLMF}:

@@

Let $b = jq$, and $w(q)$ be the \textit{Faddeeva function} \cite{NIST:DLMF}.  The integral becomes

@@

\mathcal{E}_{r * s}(t) = \frac{1}{2} | r_a(t) * s_a(t) | \label{eq:final2}

@@

@@

As above, let $b=x+\frac{1}{2}z$, and $b = j q$.  In a procedure resembling the calculation for $r_a(t) * \Re\lbrace s_a(t)\rbrace$, the result for $I(x,z)$ is

@@

I(x,z) = \frac{\sqrt{\pi}}{2} w(q)

@@

where $w(q)$ is the Faddeeva function.  Note that the Faddeeva function is \textit{entire}, meaning the $\Re\lbrace \rbrace$ operator and differentiation commute.  Inserting this result into Eq. \ref{eq:conv_sr}, and distributing the $\Re\lbrace \rbrace$ operator to the instances of $I(x,z)$, gives

@@

s * r = -\sqrt{\pi}R_0 E_0 \sigma_t^2 \\ \left(xe^{-x^2} \Re\left\lbrace w(q)\right\rbrace - \frac{1}{2}e^{-x^2} \frac{d\Re\lbrace w(q)\rbrace}{dx} \right)

@@

From the definition of $q$ and the chain rule, $dw(q)/dx = -jdw(q)/dq$, and $dw(q)/dq = -2qw(q)+2j/\sqrt{\pi}$ \cite{NIST:DLMF}.  The final result is left in terms of the real part of the Faddeeva function, which may be computed using the \textit{Voigt function} $U(x,t)$ \cite{NIST:DLMF,PhysRevD.105.123019}.
s * r = -\sqrt{\pi}R_0 E_0 \sigma_t^2 \\ \left(xe^{-x^2} \Re\left\lbrace w(q)\right\rbrace + j\frac{1}{2}e^{-x^2} \frac{d\Re\lbrace w(q)\rbrace}{dq} \right) \label{eq:final3}
\item To illustrate the accuracy and efficiency of the model, Eq. \ref{eq:final}-\ref{eq:final2} and \ref{eq:final3}, are shown in Fig. \ref{fig:fig1}.
\begin{figure}
